An algorithmic framework for generating contour parallel toolpaths with adaptive extrusion width for additive manufacturing

### 2019-08-27 4_method.tex
Tims changes to 3.5 and Juns changes to 3.6

\begin{figure}\centering
\setlength{\figwidth}{0.19\columnwidth}
\setlength{\figwidthTwo}{0.3\columnwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_mat}
\caption{Medial Axis}\label{shape_decomposition_mat}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_vd}
\caption{Voronoi Diagram}\label{shape_decomposition_vd}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_st}
\caption{Skeletal Trapezoids}\label{shape_decomposition_st}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/half_edge_datastructure.pdf}
\caption{Data structure}\label{shape_decomposition_datastructure}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/domains.pdf}
\caption{Polygon Domains}\label{shape_decomposition_domains}
\end{subfigure}
\caption{
Skeletonization of an outline shape (black).
Relation between the medial axis (red), the limited Voronoi Diagram (red and green) and the Skeletal Trapezoidation (red, green and gray): MAT $\subset$ Limited VD $\subset$ ST.
\subref{shape_decomposition_datastructure} We can represent a skeleton using a half-edge data-structure.
\subref{shape_decomposition_domains} The ST divides the shape into primitives which can be classified as belonging to one of the input shape polygons.
}
\label{skeletonization_comparison}
\end{figure}

@@

% The trapezoids are classified as belonging to a specific domain following \citeauthor{Ding2016a}.
% Each polygon in the input shape acquires it's own domain.
% The domains of hole polygons are touching the domains of the outer polygon.
% See \cref{shape_decomposition_domains}.

@@

\subsection{Center classification}\label{sec_center_classification}
%The simple technique of performing uniform width offset produces large overfill and underfill areas on central regions of the ST.
%These central regions present themselves as upper ridges in the mountains of the UoC surface.
%In order to prevent the over- and underfill we will change the bead counts in the central regions.
%This sections covers what parts of the UoC will be marked as being central.
In order to prevent over- and underfill to occur in central
\jun{TODO: For what purpose ... }
we mark parts of the UoC as being central.
The remaining is called peripheral.
Our framework will decide on a beading at all of the marked nodes in `the center' and apply the beading outward to the unmarked nodes.

@@

@@

We calculate the location $l$ of the boundary between a significant and nonsignificant portion of an edge analytically.
For example, the parabolic MAT edge generated from the outline vertex $(0,1)$ and an outline segment aligned with the X-axis follows $y(x) = \nicefrac12 x^2$ and $R(x) = y(x)$.
We can determine the significant portion $[-x_\text{bound}, x_\text{bound}]$ by evaluating $\frac{\partial R}{\partial x} > \cos(\alpha_\text{max} / 2)$, which is $ | x_\text{bound} | = (\tan(\alpha_\text{max} / 2))^{-1}$.
Similarly, a MAT edge generated from two vertices at $(0,0)$ and $(0,1)$ follows $y(x) = \nicefrac12$ and $R(x) = \sqrt{\nicefrac14 + x^2}$.
The boundaries of significance are given by $ | x_\text{bound} | = \nicefrac12 (\tan(\alpha_\text{max} / 2))^{-1}$.
From these we can derive the locations $l = (\pm x_\text{bound}, y(x_\text{bound}))$.
These specific cases can easily be transformed into all possible cases using scaling and rotation operations.

@@

\subsection{Peripheral heights}\label{sec_peripheral_height_adjustment}
Now that we have transformed the heights in the central regions of the UoC we need to determine the heights in the rest of the shape, i.e. the periphery, and slice the resulting mesh into isocontour toolpaths.
The peripheral heights could be determined in a plethora of ways according to various beading schemes.
The ramps from the outline shape to the center might have various curves,
but for our example we use straight ramps, just like the original UoC.
See \cref{peripheral_heights}.
That means we can stretch the $R$ heights of the UoC with a multiplier depending on the height of the center in terms of bead count.

@@

For the purpose of generating toolpaths we only need to define the height at the locations which will be part of a slice, rather than at all locations in the periphery.
Instead of adjusting the height of peripheral mesh nodes, we determine the locations along the edges where the adjusted height coincides with a slicing height.
In this section we will show how we can define a mapping from radial distance values to the indices of slicing heights, called a \emph{beading},
how each beading is calculated for a central node
and how the beadings are propagated outward to peripheral nodes.
This helps to define an efficient slicing algorithm in \cref{sec_toolpath_extraction}.

\begin{definition}
In order to help generate these toolpath locations we associate each central node with a mapping from radial distances to bead indices, the beading $B$,
which we define as the following set:
$$
B = \left\{ d, n, \left\{ w_0 , \dots , w_{n-1} \right\}, \left\{ l_0 , \dots , l_{n-1} \right\}  \right\}
$$
where
$d = 2 R(v)$ is the diameter associated with $v$,
$n \in \mathbb{N}$ is the bead count,
$w_i$ is the bead width of the bead with index $i$ counting from the outline inward
and
$l_i$ is the radial locations which maps to the bead with index $i$.
\end{definition}

For our example we linearly map the $R$ values using a multiplication factor of $d/n$:
\begin{align*}
w_i &= d/n  \\
l_i &= d / n (i + \nicefrac12)
\end{align*}
An example beading is visualized in the top of \cref{beading_interpolation}:
$B^V$ cover the total horizontal distance $d$ using $n=4$ beads all with the same width and radial locations $l$ evenly divided over the length $d$.

@@

\subsubsection{Beading interpolation}\label{section_beading_interpolation}
Central nodes which are in the middle of a transition have obtained a fractional bead count, but the definition of a beading presupposed integer numbers.
In order to generate a beading for a central node with a fractional bead count assigned we use the fractional part of the bead count to interpolate between two beadings defined on the fractional bead count rounded up and down.
Suppose we want to interpolate between two beadings $B^V$ and $B^W$, for which $n^{B^V} < n^{B^W}$.
We interpolate the diameter $d$, widths $w_i$ and locations $l_i$ for indices $i < \nicefrac12 n^{B^V}$ linearly and enforce the symmetry constraints on the upper indices.
See \cref{beading_interpolation}.
The linear interpolation enforces robustness against small perturbations in the outline shape which cause extra edges to appear in the ST inside of transition regions.

@@

\subsubsection{Beading propagation}\label{section_beading_conflicts}
The beading information associated with the central nodes is then propagated outward throughout the whole mesh.
However, beading conflicts can arise where a marked edge has unmarked upward edges attached to them, since beading will also be propagated down from the local maxima or other higher marked regions.
See \cref{beading_conflict_problem}.
In such a case we interpolate between the lower beading and the beading propagated from above,
starting from the lower marked node and ending at a distance $t_\text{beading}$ upward.
At the nodes in between we will apply the interpolation between the two beadings and propagate the interpolated beading outward from those nodes.
This interpolation is performed during the beading propagation algorithm.

@@

@@

@@

\begin{figure}
\centering
\includegraphics[width=.5\columnwidth]{sources/method/segment_generation.pdf}
\caption{
Generating toolpaths on a part of the test outline shape which is fully shown in \cref{shape_decomposition_domains}.
Each edge is assigned toolpath sites (yellow) which are connected together as shown in the singled out trapezoid.
By following the trapezoids along the domain (cyan) of a single outline polygon,
the extrusion segments can efficiently be connected into existing polyline toolpaths (light and dark gray).
}
\label{segment_generation}
\end{figure}

>>>>

\begin{figure}\centering
\setlength{\figwidth}{0.24\columnwidth}
\setlength{\figwidthTwo}{0.3\columnwidth}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_mat}
\caption{Medial Axis}\label{shape_decomposition_mat}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_vd}
\caption{Voronoi Diagram}\label{shape_decomposition_vd}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_st}
\caption{Skeletal Trapezoids}\label{shape_decomposition_st}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/half_edge_datastructure.pdf}
\caption{Data structure}\label{shape_decomposition_datastructure}
\end{subfigure}
\caption{
Skeletonization of an outline shape (black).
Relation between the medial axis (red), the limited Voronoi Diagram (red and green) and the Skeletal Trapezoidation (red, green and gray): MAT $\subset$ Limited VD $\subset$ ST.
\subref{shape_decomposition_datastructure} We can represent a skeleton using a half-edge data-structure.
}
\label{skeletonization_comparison}
\end{figure}

@@

@@

\subsection{Center classification}\label{sec_center_classification}
%The simple technique of performing uniform width offset produces large overfill and underfill areas on central regions of the ST.
%These central regions present themselves as upper ridges in the mountains of the UoC surface.
%In order to prevent the over- and underfill we will change the bead counts in the central regions.
%This sections covers what parts of the UoC will be marked as being central.
In order to prevent over- and underfill to occur in central, we mark parts of the UoC as being central.
The remaining is called peripheral.
Our framework will decide on a beading at all of the marked nodes in `the center' and apply the beading outward to the unmarked nodes.

@@

\jun{TODO}

@@

We calculate the location $l$ of the boundary between a significant and nonsignificant portion of an edge analytically.
For example, the parabolic MAT edge generated from the outline vertex $(0,1)$ and an outline segment aligned with the X-axis follows $y(x) = \nicefrac12 x^2$ and $R(x) = y(x)$.
We can determine the significant portion $[-x_\text{bound}, x_\text{bound}]$ by evaluating $\frac{\partial R}{\partial x} > \cos(\alpha_\text{max} / 2)$, which is $ | x_\text{bound} | = (\tan(\alpha_\text{max} / 2))^{-1}$.
Similarly, a MAT edge generated from two vertices at $(0,0)$ and $(0,1)$ follows $y(x) = \nicefrac12$ and $R(x) = \sqrt{\nicefrac14 + x^2}$.
The boundaries of significance are given by $ | x_\text{bound} | = \nicefrac12 (\tan(\alpha_\text{max} / 2))^{-1}$.
From these we can derive the locations $l = (\pm x_\text{bound}, y(x_\text{bound}))$.
These specific cases can easily be transformed into all possible cases using scaling and rotation operations.
\jun{TODO}

@@

\subsection{Peripheral Beading}\label{sec_peripheral_height_adjustment}

Now that we have transformed the heights in the central regions of the UoC we need to determine the heights in the rest of the shape, i.e. the periphery, and slice the resulting mesh into isocontour toolpaths.
The peripheral heights could be determined in a plethora of ways according to various beading schemes.
The ramps from the outline shape to the center might have various curves,
but for our example we use straight ramps, just like the original UoC.
See \cref{peripheral_heights}.
Mapping an original cone at apex $v$ to a cone with a height equal to the prescribed bead count $b$ of the central region is simply a matter of multiplying the $R$ values by $b / R(v)$.

@@

However, for the purpose of generating toolpaths we only need to define the height at the locations which will be part of a slice, rather than at all locations in the periphery.
Instead of adjusting the height of peripheral mesh nodes, we determine the radial distances where the adjusted height coincides with a slicing height.
In this section we will show how we can define a mapping from radial distance values to the indices of slicing heights, called a \emph{beading},
how each beading is calculated for a central node
and how the beadings are propagated outward to peripheral nodes.
This helps to define an efficient slicing algorithm in \cref{sec_toolpath_extraction}.

\paragraph{Beading} 
We associate each central node $v$ with a set of radial distances for each bead along with the width of that bead, which we call the \emph{beading} $B$.
For our distributed beading scheme we define the beading for a central node $v$ as:
\begin{align*}
    B &= \left\{ \left( w_0 , l_0 \right), \dots, \left( w_{n-1}, l_{n-1} \right) \right\} \\
    w_i &= 2R(v) / n  \\
    l_i &= 2R(v) / n (i + \nicefrac12)
\end{align*}
where
$w_i$ and $l_i$ are the width and location of the $i$th bead,
respectively, counting from the outline inward.
An example beading is visualized in the top of \cref{beading_interpolation}:
$B^V$ cover the total horizontal distance $d$ using $n=4$ beads all with the same width and radial locations $l$ evenly divided over the length $d$.

@@

% \subsubsection{Beading interpolation}\label{section_beading_interpolation}
\paragraph{Beading interpolation}
Central nodes which are in the middle of a transition have obtained a fractional bead count, but the definition of a beading presupposed integer numbers.
In order to generate a beading for a central node with a fractional bead count assigned we use the fractional part of the bead count to interpolate between two beadings defined on the fractional bead count rounded up and down.
Suppose we want to interpolate between two beadings $B^V$ and $B^W$, for which $n^{B^V} < n^{B^W}$.
We interpolate the diameter $d$, widths $w_i$ and locations $l_i$ for indices $i < \nicefrac12 n^{B^V}$ linearly and enforce the symmetry constraints on the upper indices.
See \cref{beading_interpolation}.
The linear interpolation enforces robustness against small perturbations in the outline shape which cause extra edges to appear in the ST inside of transition regions.

@@

% \subsubsection{Beading propagation}\label{section_beading_conflicts}
\paragraph{Beading propagation}
The beading information associated with the central nodes is then propagated outward throughout the whole mesh.
However, beading conflicts can arise where a marked edge has unmarked upward edges attached to them, since beading will also be propagated down from the local maxima or other higher marked regions.
See \cref{beading_conflict_problem}.
In such a case we interpolate between the lower beading and the beading propagated from above,
starting from the lower marked node and ending at a distance $t_\text{beading}$ upward.
At the nodes in between we will apply the interpolation between the two beadings and propagate the interpolated beading outward from those nodes.
This interpolation is performed during the beading propagation algorithm.

@@

\jun{It is more logical to first explain the general case (the above paragraph), and then the special treatment -- beading conflict.}

@@

\tim{Below is taken from an outdated paragraph in section 3.3 (?)}
The trapezoids are classified as belonging to a specific domain following \citeauthor{Ding2016a}.
Each polygon in the input shape acquires it's own domain.
The domains of hole polygons are touching the domains of the outer polygon.
See \cref{shape_decomposition_domains}.

@@

\begin{figure}
\centering
\setlength{\figheight}{.3\columnwidth}
\begin{subfigure}{.3\columnwidth}\centering
\includegraphics[height=\figheight]{sources/method/domains.pdf}
\caption{Polygon domains}\label{shape_decomposition_domains}
\end{subfigure}
\begin{subfigure}{.6\columnwidth}\centering
\includegraphics[height=\figheight]{sources/method/segment_generation.pdf}
\caption{Extrusion segment chaining}\label{shape_decomposition_domains}
\end{subfigure}
\caption{
Generating toolpaths on a part of the test outline shape by chaining together extrusion segments along each polygon domain.
Each edge is assigned toolpath sites (yellow) which are connected together as shown in the singled out trapezoid.
By following the trapezoids along the domain (cyan) of a single outline polygon,
the extrusion segments can efficiently be connected into existing polyline toolpaths (light and dark gray).
}
\label{segment_generation}
\end{figure}
